---
title: "p8105_hw1_hq2182"
author: Hanfei Qi
output: github_document
---

This is my solution to HW1.  
Load the tidyverse first.

```{r load, message = FALSE}
library(tidyverse)
```


## Problem 1

Create a data frame with specific elements according to hw requirement.

```{r dataframe}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_10 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)

# Display the table
prob1_df
```

Take the mean of each variable in my data frame.  
The warning will not be displayed.

```{r, warning = FALSE}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_10))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

Conclusion: I can take the mean of numbers and logical but not character or factor.  

Try to convert the logical, character, and factor variables to numeric variables.

```{r, warning = FALSE, results = "hide"}
as.numeric(pull(prob1_df, samp_gt_10))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

Conclusion: The logical and factor variables can be converted to numeric variables, while the character variables cannot.  

Convert variable's type and multiply the random sample by the result.  
The warning will not be displayed.

```{r, warning = FALSE}
as.numeric(pull(prob1_df, samp_gt_10)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_10)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_10))) * pull(prob1_df, samp)
```

Conclusion: I can multiply numbers with numbers but not factors with numbers.

## Problem 2

Firstly, load the library and penguins dataset.

```{r}
library("palmerpenguins")
data("penguins", package = "palmerpenguins")
```

#### A short description of the penguins data set

* The data set includes `r colnames(penguins)` of penguins.
* Example values corresponding to variable names showed above: `r head(penguins, 1)`.
* There are `r nrow(penguins)` rows and `r ncol(penguins)` columns in this data set.
* The mean of flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm.

#### Scatterplot of flipper_length_mm (y) vs bill_length_mm (x)
#### The color indicates species

Create a new data frame to collect all information I need,  
then use ggplot to make a scatterplot.  
The scatterplot will be saved as a pdf file.

```{r scatterplot, warning = FALSE}
plot_df = tibble(
  bill_length = pull(penguins, bill_length_mm),
  flipper_length = pull(penguins, flipper_length_mm),
  species = pull(penguins, species))

ggplot(
  plot_df,
  aes(x = bill_length, y = flipper_length, color = species)) + geom_point()

ggsave("p8105_hw1_scatter_plot_hq2182.pdf", height = 4, width = 6)
```
